---
title: RMarkdown demonstration
author: Finn Lindgren
date: 2020-01-28
output: pdf_document
---

This is a heading
=====

```{r results='hide'}
suppressPackageStartupMessages(library(tidyverse))
theme_set(theme_bw())
```

RMarkdown comes in to flavours: Text documents that include specially
marked chunks of R code (file ending `.Rmd`), and R scripts that include
specially marked blocks of text (file ending `.R`).
For this demonstration, we're adding blocks of code.

The following is an R code "chunk". Any output from
running the code will be typeset as well.

```{r}
cos(1)
```

The output of R code can also be included in lines of text,
like $\sin(1)=$
`r sin(1)`.
Note: RMarkdown is sometimes picky about whitespace; in this example, eliminating whitespace and having the R code start on a new line turned out to be the safest option.

This is a sub-heading
-----

This is some more text with a simple mathematical
formula, $y_i = \beta_0 + x_i \beta_1 + \epsilon_i$. The
mathematical formula syntax is essentially a subset of the powerful \LaTeX\ notation.
Larger formulas can be "displayed", using `$$` instead of `$`. For example,
$$
y_i = \beta_0 + \sum_{k=1}^p X_{ik} \beta_k + \epsilon_i .
$$

A blank line gives a new paragraph.

If we only want the result of a chunk of R code to be seen, we can add
special instructions in a comment at the beginning of the code chunk.
See [https://yihui.name/knitr/options/](https://yihui.name/knitr/options/)
for a list of all the available options!

```{r echo=FALSE}
sin(1)
```

The `echo=FALSE` option can be useful for hiding code where we only want to show the result of a computation, and note the code itself.
Another useful option is `eval=FALSE`,
which can be used for chunks of code that should be shown but not run,
perhaps to illustrate a programming error, which RMarkdown would otherwise
complain about:

```{r echo=TRUE,eval=FALSE}
curve(cos x, 0, 1)
```

We can also include R generated figures:

```{r}
ggplot(data.frame(x = seq(1e-3, pi, length.out = 1000)) %>%
         mutate(fun = cos(pi / x))) +
  geom_line(aes(x, fun))
```
